The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-10 paper/ms.tex
Add exact numbers for midplane variation of Sgr sims

We compute the same midplane variation in Figure~\ref{fig:midplane_chervin},
but for four succcessive timesteps of the live N-body simulation of a
Sagittarius encounter \citep{2018MNRAS.481..286L}. Again we have subtracted a
best fit curve of the form $\text{A} \sin{\left(\phi + \text{B}\right)} +
\text{C}$, with the values for $\text{A}$ being $9.5$, $2.5$, $-212$, and
$-394\,\pc$, for $\text{B}$ being $0.0013$, $0.0007$, $-0.63$, and
$-1.00\,\text{rad}$ and $\text{C}$ being $2.6$, $-7.8$, $-65$, and $-53\,\pc$
chronologically for each of the four timesteps shown.

@@

\item To demonstrate the previous point, we measured the local galactic
midplane along the Solar circle in three different high-resolution, zoom-in
simulations of Milky Way mass galaxies from the FIRE collaboration, as well as a controlled simulation of the interaction of the Milky Way with Sagittarius. We found
that the midplane varies as a function of azimuth at the Solar circle by
$\sim185$, $162$, $84\,\pc$ (middle $90\%$) for the three cosmological simulations we considered
(\mi{}, \mf{}, and \mm{}, respectively) and by $\sim30$ and $\sim100\,\pc$ before and after the interaction in the controlled simulation. Comparison of the corresponding velocity variations with recent measurements in the Milky Way suggests that these values are consistent with expectations for midplane variations in the Milky Way itself, which have not yet been measured as a function of azimuth.

>>>>

We compute the same midplane variation in Figure~\ref{fig:midplane_chervin},
but for four succcessive timesteps of the live N-body simulation of a
Sagittarius encounter \citep{2018MNRAS.481..286L}. Again we have subtracted a
best fit curve of the form $\text{A} \sin{\left(\phi + \text{B}\right)} +
\text{C}$, with the values for $\text{A}$ being $9.5$, $2.5$, $-212$, and
$-394\,\pc$, for $\text{B}$ being $0.0013$, $0.0007$, $-0.63$, and
$-1.00\,\text{rad}$ and $\text{C}$ being $2.6$, $-7.8$, $-65$, and $-53\,\pc$
chronologically for each of the four timesteps shown. The middle $90\%$ of midplane values across the Solar circle spans $49$, $62$, $137$, and $119\,\pc$, for each timestep.

@@

\item To demonstrate the previous point, we measured the local galactic
midplane along the Solar circle in three different high-resolution, zoom-in
simulations of Milky Way mass galaxies from the FIRE collaboration, as well as a controlled simulation of the interaction of the Milky Way with Sagittarius. We found
that the midplane varies as a function of azimuth at the Solar circle by
$\sim185$, $162$, $84\,\pc$ (middle $90\%$) for the three cosmological simulations we considered
(\mi{}, \mf{}, and \mm{}, respectively) and by $\sim60$ and $\sim120\,\pc$ before and after the interaction in the controlled simulation. Comparison of the corresponding velocity variations with recent measurements in the Milky Way suggests that these values are consistent with expectations for midplane variations in the Milky Way itself, which have not yet been measured as a function of azimuth.
